---
title: "Alcohol vs Seat choice"
author: "Lelainy Saavedra"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv") 
require(knitr)
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
$H_0$: There is a difference in where you are seated and the amount of alcohol you consume.  
$H_A$: There is No difference in the location of where you are seated and the amount of alcohol you consume.

## Now with ggplot - first select the basic data
```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```

## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=FALSE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```




## Conclusions  
We reject the null Hypothesis because the P value is less than 0.05, and go for the alternative Hypothesis instead. There is no difference in where you are seated and the amount of alcohol you consume.


